\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-24 journalWallFriction/theory2robAlgs.tex
Edited the procedure of Delta configuration space

 Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is an $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided.

 \textcolor{red}{[INSERT PROCEDURE]}\\

 \textcolor{red}{    Describe how to generate a $\Delta$ Configuration Space for polygon $P$.}

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-side reachable sets are drawn in transparent blue.
}
\end{figure}

>>>>

% $\Delta$ configuration space is a space containing all the possible relative distances for $p_1$ and $p_2$. 
Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is a $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided. 
 To give an intuition, suppose that the first particle is positioned on a vertex of the workspace. The $\Delta$ configuration space is mainly determined by moving the second particle along the edges of the workspace and considering its relative distance to the first particle.
%  what $\Delta$ configuration space is, consider the first particle on a vertex of the workspace. Now if the other particle moves on the boundary of the workspace, the relative distance between the two particles is maximized. 
In particular, to generate the $\Delta$ configuration space we iterate through all vertices $v_i$.  %In each iteration, we put the first particle at the $i^{\textrm{th}}$ vertex. 
At each iteration, we compute $v_i - v_j$  ($1 \leq j \leq n$) and then make an $n$-sided polygon according to these values. Since our current workspaces are convex, the convex hull of these  $n$-sided polygons determines the boundary of the $\Delta$ configuration space. To give a concrete example, Fig.~\ref{fig:irregular} shows an arbitrary 4-sided workspace on the left. All the 4-sided polygons made by the computation of $(v_i-v_j)$s are shown in the middle and accordingly, $\Delta$ configuration space is shown on the right with 2-move reachable sets drawn in transparent blue. We will discuss how to generate 2-step reachable sets in the following subsection.

 %\textcolor{red}{[INSERT PROCEDURE]}\\

 %\textcolor{red}{    Describe how to generate a $\Delta$ Configuration Space for polygon $P$.}

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-move reachable sets are drawn in transparent blue.
}
\end{figure}
